Globally-centered autocovariances in MCMC

### 2020-07-23 Paper/main.tex
Down to 32 pages, trimmed the edges off the appendix. Done for the day most likely

Markov chain Monte Carlo (MCMC) is a sampling method used to obtain correlated realizations from a stochastic process. Due to this serial correlation in observations, a large number of MCMC samples are required to estimate features of the target distribution as compared to the independent ones. Therefore, it becomes imperative for an MCMC practitioner to have an idea about underlying dependence structure in the Markov chains. Autocovariance function (ACF) characterizes this dependence for a stationary Markov chain. Suppose $\{X_t; t \in \mathbb{Z}\}$ is a stochastic process with mean $\mu$ and follows second-order stationarity i.e. (1) $\mathbb{E}[X_t] = \mu$ is constant for all $t$, (2) $\mathbb{E}[X_t^2]$ is constant for all $t$, and (3) $\mathbb{E}[X_t X_{t+k}]$ is a function of $k$ only $\forall k,t \in \mathbb{Z}$. Then, the autocovariance function at lag-$k$ is defined as

\[
    \Gamma(k) = \Cov(X_t, X_{t+k}) = \mathbb{E}[(X_t - \mu)(X_{t+k} - \mu)^T].
\]

@@

\begin{theorem} \label{th:G-SVE_variance}
 If Assumption \ref{ass:variance_cal} hold, $b_n^{-1}{n}\Var \left(\hat{\Sigma}_{G}^{ij} \right) = [\Sigma_{ii}\Sigma_{jj} + \Sigma_{ij}^2]\int_{-\infty}^{\infty}w(x)^2dx  + o(1)$.
\end{theorem}

@@

Suppose $\{X_t\}_{t=1}^n$ is the Markov chain of $n$ samples where $\overline{X}_n = \dfrac{1}{n}\sum_{t=1}^{n}X_t$ is the MCMC average. Let $w_k$ denote the lag-window at lag-k, i.e. $w_k = w_n(k/b_n)$. The alternate formulation for MSVE is given by

\begin{equation} \label{eq:Kyriakoulis_sv}
    \hat{\Sigma}_{SV} = \dfrac{1}{n}A^T T(w) A, \qquad \textrm{ where } A = \begin{pmatrix}
    X_1 - \overline{X}_n  & \dots & X_n - \overline{X}_n
\end{pmatrix}^T
\end{equation}

and $T(w)$ is the $n \times n$ Toeplitz matrix of weights with the first column being $w = 
\begin{pmatrix}
    1 & w_1 & w_2 & \dots w_{n-1}
\end{pmatrix}^T$.
$T(w)$ is an $n \times n$ matrix which can be difficult to store. Therefore, \cite{heberle2017fast} computed $T(w)A$ directly using an FFT based algorithm. The algorithm requires embedding $T(w)$ in a $2n \times 2n$ circulation matrix $C(w^*)$. We write the spectral decomposition of $C(w^*)$ as $V\Lambda V^*$. A is extrapolated into a $2n \times p$ matrix $A^*$ such that
\[
    \hat{\Sigma}_{SV} = \dfrac{1}{n} A^T T(w) A = \dfrac{1}{n} A^T (C(w^*) A^*)_{1:n, :} = \dfrac{1}{n} A^T (V \Lambda V^* A^*)_{1:n, :}).
\]
The complete algorithm is as follows
\\
\begin{algorithm}[H]
\DontPrintSemicolon
\SetAlgoLined

Construct $C(w^*) \textrm{ and } A^*$ from the MCMC samples.\\ Compute the DFT of the first column of $C(w^*)$. This gives the eigenvalues of $C(w^*)$.\;
\For{$j = 1, 2, ..., p$}    
    { 
    Calculate $V^*A_j^*$ by FFT of $A_j$\;
    Multiply the $i^{th}$ entry of the vector $V^* A_j^*$ with the eigenvalue $\lambda_i$ for all $i = 1, 2, ..., 2n$ in order to construct $\Lambda V^* A_j^*$.\;
    Determine $C(w^*)A^* = V \Lambda V^* A_j^*$ by inverse FFT of $\Lambda V^* A_j^*$.\;
    }
 Select the first $n$ rows of $C(w^*)A^*$ to form $T(w)A$.\;
 Premultiply by $A^T$ and divide by $n$.
 \caption{Herberle's Algorithm}
\end{algorithm}

@@

\[
\text{ESS} = mn\left(\dfrac{\abs{\Lambda_{mn}}}{\abs{\hat{\Sigma}_{G-SVE}}}\right)^{1/p}
\]

@@

\begin{figure}
 \begin{subfigure}{\textwidth}
   \centering
   \includegraphics[width=.8\linewidth]{plots/acf,n=500.pdf}
   \caption{$n = 500$}
   \label{subfig:acf-500}
\end{subfigure}\\
\begin{subfigure}{\textwidth}
  \centering
  \includegraphics[width=.8\linewidth]{plots/acf,n=10000.pdf} 
  \caption{$n = 10^4$}
  \label{subfig:acf-5e4}
\end{subfigure}
\caption{Autocorrelation plot for ACF and G-ACF for first chain out of two parallel Markov chains. First column corresponds to ACF calculated using arithmetic mean of first Markov chain and the second column corresponds to the one calculated using global mean of two Markov chains.(a): $n = 500$, not converged yet; (b): $n =  10^4$, converged}
\label{fig:var-acf}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width = .5\textwidth]{plots/var-ess.pdf}
    \caption{Running plots for $\hat{ESS}/mn$ calculated using ASV (black) and G-SVE (blue). The true $ESS/mn$ (red) is known.}
    \label{fig:var-ess}
\end{figure}

@@

We will use a bivariate bi-modal distribution introduced by \cite{gelman1991note} which has Gaussian conditional distributions in both directions. This allows us to sample parallel Markov chains using the Gibbs sampler. Let $x$ and $y$ be two random variable that are jointly distributed as 
%
\[
f(x, y) \propto \exp\left(-\dfrac{1}{2}[Ax^2y^2 + x^2 + y^2 -2Bxy  -2C_1x - 2C_2y]\right)
\]

@@

\begin{comment}
\begin{figure}[h]
    \centering
    \begin{subfigure}[h]{.4\textwidth}
        \centering
        \includegraphics[width = \textwidth]{plots/boom-pers_1_3_8.pdf}
        \caption{$A = 1, B = 3, C = 8$}
        \label{subfig:boom-pers_1_3_8}
    \end{subfigure}
    \begin{subfigure}[h]{.4\textwidth}
        \centering
        \includegraphics[width = \textwidth]{plots/boom-pers_1_10_7.pdf}
        \caption{$A = 1, B = 10, C = 7$}
        \label{subfig:boom-pers_1_10_7}
    \end{subfigure}
    \caption{Perspective plots of the target distribution for two different parameterizations.}
   \label{fig:3d_plot}
\end{figure}
\end{comment}

\begin{comment}
\begin{figure}[h]
    \centering
    \begin{subfigure}[h]{.4\textwidth}
      \centering
      \includegraphics[width = \textwidth]{plots/scatter_n1000.pdf}
      \caption{$n = 1000$}
      \label{subfig:boom-sp_1e3}
    \end{subfigure}
    \begin{subfigure}[h]{.4\textwidth}
      \centering
      \includegraphics[width = \textwidth]{plots/scatter_n50000.pdf}
      \caption{$n = 50000$}
      \label{boom-sp_1e4}
    \end{subfigure}
    \caption{The scatter plots for two parallel Markov chains. (a): Both the chains are stuck in one of the mode (b): Both the chains have travelled and explored both the modes.}
    \label{fig:boom-sp}
\end{figure}
\end{comment}

@@

\begin{figure}[h]
    \centering
    \begin{subfigure}[h]{.8\textwidth}
      \centering
      \includegraphics[width = \textwidth, height = 2in]{plots/boom-acf,n=1000.pdf}
      \caption{$n = 1000$}
      \label{subfig:boom-acf_1e3}
    \end{subfigure}
    \begin{subfigure}[h]{.8\textwidth}
      \centering
      \includegraphics[width = \textwidth, height = 2in]{plots/boom-acf,n=50000.pdf}
      \caption{$n = 50000$}
      \label{subfig:boom-acf_1e4}
    \end{subfigure}
    \caption{ACF and G-ACF for component-1 of chain-1 at two different number of Monte Carlo samples. }
    \label{fig:boom-acf}
\end{figure}

@@

\begin{table}[h]
\centering
    \begin{tabular}{p{1cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}}
    % \toprule
        n & \multicolumn{2}{|c|}{$m = 2$} & \multicolumn{2}{|c|}{$m=5$}\\
        \hline
        & ASV & G-SVE & ASV & G-SVE\\
        \hline
        $10^3$ & 0.612 & 0.689 & 0.602 & 0.753   \\
        $2\cdot10^3$ & 0.693 & 0.751 & 0.735 & 0.827 \\
        $5 \cdot 10^3$  & 0.826 & 0.854 & 0.847 & 0.880 \\
        $10^4$  & 0.862 & 0.868 & 0.884 & 0.907 \\
        $2 \cdot 10^4$ & 0.899 & 0.906 & 0.922 & 0.934  \\
    % \bottomrule
    \end{tabular}
    \caption{Coverage probabilities for parameter values $A = 1,\; B = 3,\; C = 8$. }
    \label{table:boom-coverage_1_3_8}
\end{table}

@@

\begin{figure}[h]
    \centering

    \begin{subfigure}[h]{.3\textwidth}
      \centering
      \includegraphics[width = \textwidth]{plots/boom-ess1.pdf}
      \caption{$A = 1, \; B = 3, \; C = 8$}
      \label{subfig:boom-ess1}
    \end{subfigure}

    \begin{subfigure}[h]{.3\textwidth}
      \centering
      \includegraphics[width = \textwidth]{plots/boom-ess2.pdf}
      \caption{$A = 1, \; B=10, \; C = 7 $}
      \label{subfig:boom-ess2}
    \end{subfigure}
    \caption{Running plot for $\hat{ESS}/mn$ using A-SVE and G-SVE calculated for two chains for two different parameterizations.}
    \label{fig:boom-ess}
\end{figure}

@@

\begin{table}[h]
\centering
    \begin{tabular}{p{1cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}}
    % \toprule
        n & \multicolumn{2}{|c|}{$m = 2$} & \multicolumn{2}{|c|}{$m=5$}\\
        \hline
        & ASV & G-SVE & ASV & G-SVE\\
        \hline
        $10^3$ & 0.873 & 0.884 & 0.875 & 0.898   \\
        $2\cdot10^3$ & 0.881 &  0.888 & 0.897    & 0.914     \\
        $5 \cdot 10^3$  & 0.902 & 0.908 &  0.919 & 0.929\\
        $10^4$  & 0.923 & 0.927 & 0.925 & 0.926 \\
        $5 \cdot 10^4$ & 0.951& 0.952 & 0.939 & 0.939  \\
    % \bottomrule
    \end{tabular}
    \caption{Coverage probabilities for parameter values $A = 1,\; B = 10,\; C = 7$. }
    \label{table:boom-coverage_1_10_7}
\end{table}

@@

For our third example, we consider a real-life problem of sensor locations previously discussed by \cite{ihler2005nonparametric}. The goal is to identify unknown sensor locations using noisy distance data. This problem is specifically interesting in our case because the joint posterior distribution for missing sensor locations is multi-modal. \\

\cite{tak2018repelling} modified the simulation settings of \cite{lan2014wormhole} to include only six sensor locations (four unknown and two unknown) out of eleven locations (eight known and three unknown). Following \cite{tak2018repelling}, we assume that there are six sensors scattered on a planar region where $x_i = (x_{i1}, x_{i2})^T$ denote the $2d$ coordinates of $i^{th}$ sensor. Let $y_{ij} = (y_{ji})$ denote the distance between the sensors $x_i$ and $x_j$. The distance between $x_i$ and $x_j$ is observed with probability $\pi (x_i, x_j) = \exp{\|x_i - x_j\|^2 / 2R^2}$ and with a Gaussian measurement error of $\sigma^2$. Let $z{ij}$ denote the indicator variable which is equal to 1 when the distance between $x_i$ and $x_j$ is observed. The probability model is then,

\begin{align*}
    z_{ij}|x_1, ..., x_6 &\sim Bernoulli\left(\exp\left(\dfrac{-\|x_i - x_j\|^2}{2R^2}\right)\right)\\
    y_{ij}| w_{ij} = 1, x_1, ..., x_6 &\sim N(\|x_i - x_j\|^2, \sigma^2)
\end{align*}

\cite{ahn2013distributed} suggested the value of $R = 0.3$ and $\sigma = 0.02$. We use a Gaussian prior for the unknown locations with  mean equal to $(0,0)$ and covariance matrix equal to $100 I_2$. $y_{ij}$ is specified only if $w_{ij} = 1$. The likelihood function is then,

\begin{multline*}
    L(x_1, x_2, x_3, x_4) \propto \\
\prod_{j>i} \left[ \left(\exp\left(\dfrac{-\|x_i - x_j\|^2}{2 \times 0.3^2}\right)\right)^{w_{ij}} \left(1 - \exp\left(\dfrac{-\|x_i - x_j\|^2}{2 \times 0.3^2}\right)\right)^{1 - w_{ij}} \exp \left(-\dfrac{y_{ij} - \|x_i - x_j\|^2}{2 \times 0.02^2}\right)\right]    
\end{multline*}

@@

\section{Preliminaries} \label{apdx:preliminaries}

@@

\section{Proof of Theorems} \label{appendix:A}

\subsection{Bias of Theorem~\ref{th:G-_expec}} 
\label{appendix:bias}

% \begin{lemma} \label{lemma:bias1}
% $\mathbb{E}\left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right] = \dfrac{m-1}{mn}\left(\sum\limits_{k=0}^{n-1}\Gamma(k) - \Sigma\right)$
% \end{lemma}
% \begin{proof}
% \begin{align*}
%     &\mathbb{E} \left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right]\\
%      &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E}\left[X_{11}\bar{\bar{X}}^T \right] + \mathbb{E} \left[\bar{X}_1\bar{\bar{X}}^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
%     &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{1}{m}\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{m-1}{m}\mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \dfrac{1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right] + \dfrac{m-1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
%     &= \dfrac{m-1}{m}\left(\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\right)\\
%     &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{t=1}^{n}\mathbb{E} \left[X_{11}X_{1t}^T \right] - \mathbb{E}\left[X_{11}\right] \mathbb{E}\left[\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\right]\mathbb{E}\left[\bar{X}_2^T\right] - \text{Var}\left[\bar{X}_1 \right] - \mathbb{E}\left[\bar{X}_1 \right]\mathbb{E}\left[\bar{X}_1^T \right]\right)\\
%     &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{k=0}^{n-1}\Gamma(k) + \mu \mu^T - \mu \mu^T + \mu \mu^T - \text{Var}\left[\bar{X}_1 \right] - \mu \mu^T\right)\\
%     &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - n\text{Var}\left[\bar{X}_1 \right]\right)\,.
% \end{align*}
% %
% Similarly,
% %    
% \begin{align*}
%     \mathbb{E} \left[ \left(\bar{X}_1 - \bar{\bar{X}} \right)  \left(X_{11} - \bar{X}_1 \right)^T \right] &= \mathbb{E}\left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right]^T = \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma \right)^T\,.
%     % &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma \right)\\
% \end{align*}
% \end{proof}

@@

  &= \dfrac{1}{n}  \left \|\sum_{t=1}^{n}X_{st} - n\mu \pm L B(n) \right\|\\

@@

  &< \dfrac{D\psi(n)}{n} + \dfrac{1}{n}\|L\| \left(\sum\limits_{i=1}^{p}|B^{(i)}(k)|^2\right)^{1/2}\\

@@

   & = \left|\dfrac{1}{m}\sum _{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\sum_{t=1}^{n-|k|} \dfrac{1}{n}\left[ \left(X_{st} - \mu \right)_i  \left(\mu-\bar{\bar{X}} \right)_j + \left(\mu-\bar{\bar{X}} \right)_i  \left(X_{s(t+k)} - \mu \right)_j\right]\right\}\right| \\

>>>>

Markov chain Monte Carlo (MCMC) is a sampling method used to obtain correlated realizations from a stochastic process. Due to this serial correlation in observations, a large number of MCMC samples are required to estimate features of the target distribution as compared to the independent ones. Therefore, it becomes imperative for an MCMC practitioner to have an idea about underlying dependence structure in the Markov chains. Autocovariance function (ACF) characterizes this dependence for a stationary Markov chain. Suppose $\{X_t; t \in \mathbb{Z}\}$ is a stochastic process with mean $\mu$ and follows second-order stationarity i.e. (1) $\mathbb{E}[X_t] = \mu$ is constant for all $t$, (2) $\mathbb{E}[X_t^2]$ is constant for all $t$, and (3) $\mathbb{E}[X_t X_{t+k}]$ is a function of $k$ only $\forall k,t \in \mathbb{Z}$. Then, the autocovariance function at lag-$k$ is defined as
%
\[
    \Gamma(k) = \Cov(X_t, X_{t+k}) = \mathbb{E}[(X_t - \mu)(X_{t+k} - \mu)^T].
\]

@@

\begin{theorem} \label{th:G-SVE_variance}
 If Assumption \ref{ass:variance_cal} holds, $b_n^{-1}{n}\Var \left(\hat{\Sigma}_{G}^{ij} \right) = [\Sigma_{ii}\Sigma_{jj} + \Sigma_{ij}^2]\int_{-\infty}^{\infty}w(x)^2dx  + o(1)$.
\end{theorem}

@@

Suppose $\{X_t\}_{t=1}^n$ is the Markov chain of $n$ samples where $\overline{X}_n = \dfrac{1}{n}\sum_{t=1}^{n}X_t$ is the MCMC average. Let $w_k$ denote the lag-window at lag-k, i.e. $w_k = w_n(k/b_n)$. The alternate formulation for MSVE is given by
%
\[
    \hat{\Sigma}_{SV} = \dfrac{1}{n}A^T T(w) A, \qquad \textrm{ where } A = \begin{pmatrix}
    X_1 - \overline{X}_n  & \dots & X_n - \overline{X}_n
\end{pmatrix}^T
\]

and $T(w)$ is the $n \times n$ Toeplitz matrix of weights with the first column being $(1 ~ w_1 ~ w_2 ~ \dots, ~ w_{n-1})^T$
%  $w = 
% \begin{pmatrix}
%     1 & w_1 & w_2 & \dots w_{n-1}
% \end{pmatrix}^T$.
$T(w)$ is an $n \times n$ matrix which can be difficult to store. Therefore, \cite{heberle2017fast} computed $T(w)A$ directly using an FFT based algorithm. The algorithm requires embedding $T(w)$ in a $2n \times 2n$ circulation matrix $C(w^*)$. We write the spectral decomposition of $C(w^*)$ as $V\Lambda V^*$. A is extrapolated into a $2n \times p$ matrix $A^*$ such that
\[
    \hat{\Sigma}_{SV} = \dfrac{1}{n} A^T T(w) A = \dfrac{1}{n} A^T (C(w^*) A^*)_{1:n, :} = \dfrac{1}{n} A^T (V \Lambda V^* A^*)_{1:n, :}).
\]
The complete algorithm is as follows

\begin{algorithm}[htbp]
\DontPrintSemicolon
\SetAlgoLined
Construct $C(w^*) \textrm{ and } A^*$ from the MCMC samples.\\ Compute the DFT of the first column of $C(w^*)$. This gives the eigenvalues of $C(w^*)$.\;
\For{$j = 1, 2, ..., p$}    
    { 
    Calculate $V^*A_j^*$ by FFT of $A_j$\;
    Multiply the $i^{th}$ entry of the vector $V^* A_j^*$ with the eigenvalue $\lambda_i$ for all $i = 1, 2, ..., 2n$ in order to construct $\Lambda V^* A_j^*$.\;
    Determine $C(w^*)A^* = V \Lambda V^* A_j^*$ by inverse FFT of $\Lambda V^* A_j^*$.\;
    }
 Select the first $n$ rows of $C(w^*)A^*$ to form $T(w)A$.\;
 Premultiply by $A^T$ and divide by $n$.
 \caption{Herberle's Algorithm}
\end{algorithm}

@@

\[
\text{ESS} = mn\left(\dfrac{\abs{\Lambda_{mn}}}{\abs{\hat{\Sigma}_{G}}}\right)^{1/p}
\]

@@

\begin{figure}[htbp]
 \begin{subfigure}{\textwidth}
   \centering
   \includegraphics[width=.6\linewidth]{plots/acf,n=500.pdf}
   \caption{$n = 500$}
   \label{subfig:acf-500}
\end{subfigure}\\
\begin{subfigure}{\textwidth}
  \centering
  \includegraphics[width=.6\linewidth]{plots/acf,n=10000.pdf} 
  \caption{$n = 10^4$}
  \label{subfig:acf-5e4}
\end{subfigure}
\caption{Autocorrelation plot for ACF and G-ACF for first chain out of two parallel Markov chains. First column corresponds to ACF calculated using arithmetic mean of first Markov chain and the second column corresponds to the one calculated using global mean of two Markov chains.(a): $n = 500$, not converged yet; (b): $n =  10^4$, converged}
\label{fig:var-acf}
\end{figure}

\begin{figure}[htbp]
    \centering
    \includegraphics[width = .35\textwidth]{plots/var-ess.pdf}
    \caption{Running plots for $\hat{\text{ESS}}/mn$ calculated using ASV and G-SVE with the truth.}
    \label{fig:var-ess}
\end{figure}

@@

We will use a bivariate bi-modal distribution introduced by \cite{gelman1991note} which has Gaussian conditional distributions in both directions. This allows us to sample parallel Markov chains using the Gibbs sampler. Let $x$ and $y$ be two random variable that are jointly distributed as 
%
\[
f(x, y) \propto \exp\left(-\dfrac{1}{2} \left[Ax^2y^2 + x^2 + y^2 -2Bxy  -2C_1x - 2C_2y  \right]\right)
\]

@@

\begin{comment}
\begin{figure}[htbp]
    \centering
    \begin{subfigure}[h]{.4\textwidth}
        \centering
        \includegraphics[width = \textwidth]{plots/boom-pers_1_3_8.pdf}
        \caption{$A = 1, B = 3, C = 8$}
        \label{subfig:boom-pers_1_3_8}
    \end{subfigure}
    \begin{subfigure}[h]{.4\textwidth}
        \centering
        \includegraphics[width = \textwidth]{plots/boom-pers_1_10_7.pdf}
        \caption{$A = 1, B = 10, C = 7$}
        \label{subfig:boom-pers_1_10_7}
    \end{subfigure}
    \caption{Perspective plots of the target distribution for two different parameterizations.}
   \label{fig:3d_plot}
\end{figure}
\end{comment}

\begin{comment}
\begin{figure}[htbp]
    \centering
    \begin{subfigure}[h]{.4\textwidth}
      \centering
      \includegraphics[width = \textwidth]{plots/scatter_n1000.pdf}
      \caption{$n = 1000$}
      \label{subfig:boom-sp_1e3}
    \end{subfigure}
    \begin{subfigure}[h]{.4\textwidth}
      \centering
      \includegraphics[width = \textwidth]{plots/scatter_n50000.pdf}
      \caption{$n = 50000$}
      \label{boom-sp_1e4}
    \end{subfigure}
    \caption{The scatter plots for two parallel Markov chains. (a): Both the chains are stuck in one of the mode (b): Both the chains have travelled and explored both the modes.}
    \label{fig:boom-sp}
\end{figure}
\end{comment}

@@

\begin{figure}[htbp]
    \centering
    \begin{subfigure}[h]{.8\textwidth}
      \centering
      \includegraphics[width = .8\textwidth]{plots/boom-acf,n=1000.pdf}
      \caption{$n = 1000$}
      \label{subfig:boom-acf_1e3}
    \end{subfigure}
    \begin{subfigure}[h]{.8\textwidth}
      \centering
      \includegraphics[width = .8\textwidth]{plots/boom-acf,n=50000.pdf}
      \caption{$n = 50000$}
      \label{subfig:boom-acf_1e4}
    \end{subfigure}
    \caption{ACF and G-ACF for component-1 of chain-1 at two different number of Monte Carlo samples. }
    \label{fig:boom-acf}
\end{figure}

@@

\begin{table}[htbp]
\centering
    \begin{tabular}{|c|l|l|l|l|}
    % \toprule
    \hline
        $n$ & \multicolumn{2}{|c|}{$m = 2$} & \multicolumn{2}{|c|}{$m=5$}\\
        \hline
        & ASV & G-SVE & ASV & G-SVE\\
        \hline
        $1000$ & 0.612 & 0.689 & 0.602 & 0.753   \\
        $2000$ & 0.693 & 0.751 & 0.735 & 0.827 \\
        $5000$  & 0.826 & 0.854 & 0.847 & 0.880 \\
        $10000$  & 0.862 & 0.868 & 0.884 & 0.907 \\
        $20000$ & 0.899 & 0.906 & 0.922 & 0.934  \\ \hline
    % \bottomrule
    \end{tabular}
    \caption{Coverage probabilities for parameter values $A = 1,\; B = 3,\; C = 8$. }
    \label{table:boom-coverage_1_3_8}
\end{table}

@@

\begin{figure}[htbp]
    \centering

    \begin{subfigure}[h]{.3\textwidth}
      \centering
      \includegraphics[width = 1.1\textwidth]{plots/boom-ess1.pdf}
      \caption{$A = 1, \; B = 3, \; C = 8$}
      \label{subfig:boom-ess1}
    \end{subfigure} \hspace{1cm}
    \begin{subfigure}[h]{.3\textwidth}
      \centering
      \includegraphics[width = 1.1\textwidth]{plots/boom-ess2.pdf}
      \caption{$A = 1, \; B=10, \; C = 7 $}
      \label{subfig:boom-ess2}
    \end{subfigure}
    \caption{Running plot for $\hat{\text{ESS}}/mn$ using ASV and G-SVE  for $m = 2$.}
    \label{fig:boom-ess}
\end{figure}

@@

\begin{table}[htbp]
\centering
    \begin{tabular}{|c|l|l|l|l|}
    % \toprule
    \hline
        $n$ & \multicolumn{2}{|c|}{$m = 2$} & \multicolumn{2}{|c|}{$m=5$}\\
        \hline
        & ASV & G-SVE & ASV & G-SVE\\
        \hline
        $10000$ & 0.873 & 0.884 & 0.875 & 0.898   \\
        $2000$ & 0.881 &  0.888 & 0.897    & 0.914     \\
        $5000$  & 0.902 & 0.908 &  0.919 & 0.929\\
        $10000$  & 0.923 & 0.927 & 0.925 & 0.926 \\
        $50000$ & 0.951& 0.952 & 0.939 & 0.939  \\ \hline
    % \bottomrule
    \end{tabular}
    \caption{Coverage probabilities for parameter values $A = 1,\; B = 10,\; C = 7$. }
    \label{table:boom-coverage_1_10_7}
\end{table}

@@

For our third example, we consider a real-life problem of sensor locations previously discussed by \cite{ihler2005nonparametric}. The goal is to identify unknown sensor locations using noisy distance data. This problem is specifically interesting in our case because the joint posterior distribution for missing sensor locations is multi-modal.

\cite{tak2018repelling} modified the simulation settings of \cite{lan2014wormhole} to include only six sensor locations (four unknown and two unknown) out of eleven locations (eight known and three unknown). Following \cite{tak2018repelling}, we assume that there are six sensors scattered on a planar region where $x_i = (x_{i1}, x_{i2})^T$ denote the $2d$ coordinates of $i^{th}$ sensor. Let $y_{ij} = (y_{ji})$ denote the distance between the sensors $x_i$ and $x_j$. The distance between $x_i$ and $x_j$ is observed with probability $\pi (x_i, x_j) = \exp{\|x_i - x_j\|^2 / 2R^2}$ and with a Gaussian measurement error of $\sigma^2$. Let $z{ij}$ denote the indicator variable which is equal to 1 when the distance between $x_i$ and $x_j$ is observed. The probability model is then,
%
\begin{align*}
    z_{ij} \mid x_1, ..., x_6 &\ sim \text{Bernoulli}\left(\exp\left(\dfrac{-\|x_i - x_j\|^2}{2R^2}\right)\right)\\
    y_{ij} \mid w_{ij} = 1, x_1, ..., x_6 &\sim N(\|x_i - x_j\|^2, \sigma^2)
\end{align*}
%
\cite{ahn2013distributed} suggested the value of $R = 0.3$ and $\sigma = 0.02$. We use a Gaussian prior for the unknown locations with  mean equal to $(0,0)$ and covariance matrix equal to $100 I_2$. $y_{ij}$ is specified only if $w_{ij} = 1$. The likelihood function is then,
%
\begin{multline*}
    L(x_1, x_2, x_3, x_4) \propto \\
\prod_{j>i} \left[ \left(\exp\left(\dfrac{-\|x_i - x_j\|^2}{2 \times 0.3^2}\right)\right)^{w_{ij}} \left(1 - \exp\left(\dfrac{-\|x_i - x_j\|^2}{2 \times 0.3^2}\right)\right)^{1 - w_{ij}} \exp \left(-\dfrac{y_{ij} - \|x_i - x_j\|^2}{2 \times 0.02^2}\right)\right]    
\end{multline*}

@@

\section{Appendix}  \label{sec:appendix}
\subsection{Preliminaries} \label{apdx:preliminaries}

@@

% \section{Proof of Theorems} \label{appendix:A}

\subsection{Proof of Theorem~\ref{th:G-_expec}} 
\label{appendix:bias}

 % \begin{proof}[Proof of Theorem~\ref{th:G-_expec}]
% \begin{lemma} \label{lemma:bias1}
% $\mathbb{E}\left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right] = \dfrac{m-1}{mn}\left(\sum\limits_{k=0}^{n-1}\Gamma(k) - \Sigma\right)$
% \end{lemma}
% \begin{proof}
% \begin{align*}
%     &\mathbb{E} \left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right]\\
%      &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E}\left[X_{11}\bar{\bar{X}}^T \right] + \mathbb{E} \left[\bar{X}_1\bar{\bar{X}}^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
%     &= \mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{1}{m}\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \dfrac{m-1}{m}\mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \dfrac{1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right] + \dfrac{m-1}{m}\mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\\
%     &= \dfrac{m-1}{m}\left(\mathbb{E} \left[X_{11}\bar{X}_1^T \right] - \mathbb{E} \left[X_{11}\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\bar{X}_2^T \right] - \mathbb{E} \left[\bar{X}_1\bar{X}_1^T \right]\right)\\
%     &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{t=1}^{n}\mathbb{E} \left[X_{11}X_{1t}^T \right] - \mathbb{E}\left[X_{11}\right] \mathbb{E}\left[\bar{X}_2^T \right] + \mathbb{E} \left[\bar{X}_1\right]\mathbb{E}\left[\bar{X}_2^T\right] - \text{Var}\left[\bar{X}_1 \right] - \mathbb{E}\left[\bar{X}_1 \right]\mathbb{E}\left[\bar{X}_1^T \right]\right)\\
%     &= \dfrac{m-1}{m}\left(\dfrac{1}{n}\sum_{k=0}^{n-1}\Gamma(k) + \mu \mu^T - \mu \mu^T + \mu \mu^T - \text{Var}\left[\bar{X}_1 \right] - \mu \mu^T\right)\\
%     &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - n\text{Var}\left[\bar{X}_1 \right]\right)\,.
% \end{align*}
% %
% Similarly,
% %    
% \begin{align*}
%     \mathbb{E} \left[ \left(\bar{X}_1 - \bar{\bar{X}} \right)  \left(X_{11} - \bar{X}_1 \right)^T \right] &= \mathbb{E}\left[ \left(X_{11} - \bar{X}_1 \right) \left(\bar{X}_1 - \bar{\bar{X}} \right)^T \right]^T = \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma \right)^T\,.
%     % &= \dfrac{m-1}{mn}\left(\sum_{k=0}^{n-1}\Gamma(k) - \Sigma \right)\\
% \end{align*}
% \end{proof}

@@

  % &= \dfrac{1}{n}  \left \|\sum_{t=1}^{n}X_{st} - n\mu \pm L B(n) \right\|\\

@@

  &< \dfrac{D\psi(n)}{n} + \dfrac{1}{n}\|L\| \left(\sum\limits_{i=1}^{p}|B^{(i)}(n)|^2\right)^{1/2}\\

@@

   % & = \left|\dfrac{1}{m}\sum _{s=1}^{m}\left\{\sum_{k=-b_n+1}^{b_n-1}w\left(\dfrac{k}{b_n}\right)\sum_{t=1}^{n-|k|} \dfrac{1}{n}\left[ \left(X_{st} - \mu \right)_i  \left(\mu-\bar{\bar{X}} \right)_j + \left(\mu-\bar{\bar{X}} \right)_i  \left(X_{s(t+k)} - \mu \right)_j\right]\right\}\right| \\
